---
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
linestretch: 2 
header-includes:
  - \fontsize{8}{20}
  - \pagenumbering{gobble} 
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
# Run analyses
source("../analysis/load_results.R")
```

## Figure legends
Fig. 1. Map of study area showing location and source of samples. The bold region in the inset denotes the area where *Carcharhinus limbatus* were sampled from in this study. The grey-shaded regions denote sampling areas for *Carcharhinus tilstoni* in previous studies in Queensland (Qld) (Harry *et al.* 2013) and the Northern Territory (NT) (Stevens and Wiley 1986). NSW, New South Wales. 

Fig. 2. Length structure and source of *C. limbatus* samples used in the present study.

Fig. 3. Age and growth of *C. limbatus*. Panels (a) and (b) show length at age. Line and shaded area are the fitted growth model with 95% confidence and prediction intervals. Panel (c) shows length of neonate sharks (known age 0) used to jointly estimate length-at-birth in the growth model. Data from Qld *C. tilstoni* (Harry *et al.* 2013) are provided for comparison in panels (a), (b) and (c). Panel (d) shows growth model residuals. Panel (e) compares growth model estimates of mean length at age for *C. limbatus* and two *C. tilstoni* populations. Panel (f) compares the growth model from (a) and (b) with the length structure of neonates and juveniles from Moreton Bay. Colours denote possible cohorts. 

Fig. 4. Weight at length of *C. limbatus*. Panel (a) shows mean weight at length with 95% confidence and prediction intervals estimated using log-linear regression. Panel (b) compares log-transformed weight at length with QLD *C. tilstoni* (Harry *et al.* 2013). 

Fig. 5. Maturity at length and age of *C. limbatus*. Panels (a) and (b) show logistic regression models with 95% confidence intervals used to estimate length and age at maturity. Points are empirical proportion of individuals mature at length and age. Panels (c) and (d) compare length and age at 50% maturity and maternity of *C. limbatus* with two populations of *C. tilstoni* (Stevens and Wiley 1986; Davenport and Stevens 1988; Harry *et al.* 2013). 

Fig. 6. Comparative demography of *C. limbatus* and *C. tilstoni*. Panel (a) is a density plot of intrinsic rate of population increase, *r*, based on 1000 Monte Carlo simulations. Panel (b) shows the mean and 95% quantiles of *r* and values assumed for natural mortality, *M*, from Monte Carlo simulation. Solid lines show how *r* varies as a function of *M* when all other variables are held equal, illustrating the range of plausible values for both quantities. Separate lines show the change when biennial or triennial reproduction is assumed for *C. limbatus*. Panels (c) and (d) are biomass-weighted stable age distributions as a function of age and length. Darker shaded regions show the proportion of mature biomass for males, and mature and maternal biomass for females. Females in maternal condition are those that would have contributed to recruitment within a given year. 

\newpage


## Figures

\
```{r fig1, fig.width = 6, fig.height = 6}
# Get map data
# getNOAA.bathy(lon1 = 150.5, lon2 = 155.5, lat1 = -27, lat2 = -32, 
# resolution = 1) %>% fortify.bathy %>% write_csv("../data/bounds.csv")
bounds <- read_csv("../data/bounds.csv")

# Points for plotting
points <- select(data, Source, Lat, Long, Depth, STL) %>% na.omit() %>%
  add_row(Source = "QLD: 2004 - 2007", Lat = -27-24/60, Long = 153 +12/60) %>%
  droplevels()
  
# Points with a coordinate system
points2 <- st_as_sf(points, coords = c("Long", "Lat"), crs = 4326)

# NSW QLD border

# coast_bbox <- st_as_sf(bounds, coords = c("x", "y"), crs = 4326) %>% st_bbox()
# coast <- st_read(here("data", "COM20111216_ELB_region.shp")) %>%
#   st_as_sf(crs = 4326) %>% 
#   select(STATE) %>% 
#   filter(STATE %in% c("NSW", "QLD")) %>%
#   group_by(STATE) %>% 
#   st_make_valid() %>% 
#   summarise() %>%
#   st_set_crs(4326) %>% 
#   st_crop(coast_bbox) %>% 
#   st_write("../data/border.shp")

coast <- st_read("../data/border.shp", quiet = TRUE)

# Map inset
aus<-map_data("world") %>% filter(region %in% "Australia")
inset <- ggplot() + geom_polygon(data = aus, aes(x = long, y = lat, group = group), fill = "grey90",
  col = "black", size = 0.25) + coord_equal() + 
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(), 
  axis.ticks = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank(), panel.border =
  element_rect(colour = "black",  fill =   "transparent"), panel.grid = element_blank(), panel.background =
  element_rect(fill = "white"), plot.background = element_blank()) + xlim(112, 157) + ylim(-45, -8) +
  geom_rect(aes(xmin = 150.5,xmax = 155.5, ymin = -32, ymax = -27), 
            col = "red", fill = "red", alpha = 0, linetype = 1, size = 0.70) + 
  geom_rect(aes(xmin = 144, xmax = 155.5, ymin = -26.5, ymax = -14),
            col = "black", fill = "black", linetype = 1, size = 0.25, alpha = 0.05) +
  annotate("text", x = 150, y= -11, label = "Qld", size = rel(3.5)) +
  geom_rect(aes(xmin = 128, xmax = 141, ymin=-13, ymax = -8),
            col = "black", fill = "black", linetype=1, size = 0.25, alpha = 0.05) +
  annotate("text", x = 123, y = -10, label = "NT", size = rel(3.5))

# Main map
p <- ggplot() + scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  #geom_raster(data = bounds[bounds$z >= 0, ], aes(x = x, y = y), fill = "grey90") +
  #geom_raster(data = bounds[bounds$z <= 0, ], aes(x = x, y = y, fill = z), guide = "none", alpha = 0.75) +
  scale_fill_gradient2(low = "#74a9cf", mid = "#bdc9e1", high = "#f1eef6") +
  geom_contour(data = bounds[bounds$z <=0, ], aes(x = x, y = y, z = z), 
  colour = "grey80", size = 0.2, breaks = c(0, -50, -100, -200, -500, -1000, -2000, - 4000)) +
  #geom_contour(data = bounds, aes(x = x, y = y, z = z), colour = "black", linetype = "solid",
  #size = 0.25, breaks = 0, alpha = 1) + 
  #geom_path(data = ozdata, aes(x = long, y= lat, group = state), col = "black", fill = "transparent") +
  geom_sf(data = coast, color = "black", fill = "grey95", size = 0.25) + 
  geom_sf(data = points2, aes(linetype = Source),  color = "transparent") +
  geom_point(data = points, aes(x = Long, y = Lat, fill = Source, shape = Source), size = 2) + 
  scale_fill_manual(values = c("#ffffcc", "#225ea8","#a1dab4")) + 
  scale_shape_manual(values = c(21, 22, 23)) + 
  guides(fill = guide_legend("Source"), colour =  guide_legend("Source"), linetype = "none") +
  xlab("") + ylab("") + 
  theme(legend.position = c(0.2, 0.2), 
        legend.background = element_rect(colour = "black"),
        legend.key = element_blank(),
  panel.background = element_rect(fill = NA),
  panel.border = element_rect(colour = "black", fill = "transparent"),
  panel.grid.major = element_line(color = "transparent"), panel.grid.minor = element_blank()) +
  annotate(geom = "text", y = -29.9, x = 151.5, label = "New South Wales", size = 5) +
  annotate(geom = "text", y = -27.25, x = 151.5, label = "Queensland", size = 5)


# Plot
v1<-viewport(width = 1, height = 1, x = 0.5, y = 0.5) #plot area for the main map
v2<-viewport(width = 0.35, height = 0.35, x = 0.35,y = 0.7) #plot area for the inset map
print(p,vp = v1)
print(inset,vp = v2)

# Clean up environment
rm(bounds, points, aus, inset, p, v1, v2)
```
\
Fig. 1

\newpage
```{r fig2, fig.width = 8, fig.height = 3.5}
h_lab <- group_by(data, Sex, Source) %>% summarise(n = n()) %>%
  mutate(label = paste(Source, " (", n, ")", sep = "")) %>% ungroup %>% select(label) %>% unlist

p <- ggplot(filter(data, Sex == "Female"), aes(x = STL, fill = Source)) +
  guides(fill = guide_legend(title = NULL)) + geom_histogram(binwidth = 10, col = "black") +
  facet_wrap(~ facet, scales = "free_y") + scale_fill_manual(values = c("#ffffcc", "#a1dab4", "#41b6c4", "#225ea8"), labels = 
  c(h_lab[[1]], h_lab[[2]], h_lab[[3]], h_lab[[4]])) + xlab("") + ylab("Numbers") + ylim(0, 65) + xlim(50, 270) +
  theme(legend.position = c(0.72, 0.74)) + lim_theme

p1 <- ggplot(filter(data, Sex == "Male"), aes(x = STL, fill = Source)) +
  guides(fill = guide_legend(title = NULL)) + geom_histogram(binwidth = 10, col = "black") +
  facet_wrap(~ facet, scales = "free_y") + scale_fill_manual(values = c("#ffffcc", "#a1dab4", "#41b6c4", "#225ea8"), labels = 
  c(h_lab[[5]], h_lab[[6]], h_lab[[7]], h_lab[[8]])) + xlab("") + ylab("") + ylim(0, 65) + xlim(50, 270) +
  theme(legend.position = c(0.72, 0.74)) + lim_theme

grid.arrange(p, p1, nrow = 1, bottom = "TL (cm)")

# Clean up environment
rm(h_lab, p, p1)
```
\
Fig 2.

\newpage

```{r fig3, fig.width = 8, fig.height = 10}
# Age and growth plots
p <- ggplot(data = filter(preds, sex == "(a) Female"), aes(x = age, y = len)) + 
  geom_ribbon(aes(ymin = plower, ymax = pupper),fill = "grey80") +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "grey60") + geom_line() +
  facet_wrap(~ sex) + geom_point(data = filter(raw_points, sex == "(a) Female"), aes(x = age,
  y= len, fill = species), shape = 21) + scale_fill_manual(values = c("#a1dab4", "#41b6c4")) + 
  xlab("Age (years)") + ylab("Total lenth (cm)") + theme(legend.position = "none") + lim_theme

p1 <- ggplot(data = filter(preds, sex == "(b) Male"), aes(x = age, y = len)) + 
  geom_ribbon(aes(ymin = plower, ymax = pupper),fill = "grey80") +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "grey60") + geom_line() +
  facet_wrap(~sex) + geom_point(data = filter(raw_points, sex == "(b) Male"), aes(x = age,
  y= len, fill = species), shape = 21) + scale_fill_manual(values = c("#a1dab4", "#41b6c4")) +  
  guides(fill = guide_legend(title = NULL)) +
  xlab("Age (years)") + ylab("TL (cm)") + 
  theme(legend.position = c(0.77, 0.18), legend.text = element_text(face = "italic", size = rel(0.75))) +
  lim_theme

df <- data_frame(x = c(preds$lower[1], preds$lower[1], preds$upper[1], preds$upper[1]), y = c(0, Inf, 0, Inf))

p2 <- ggplot(data = len0_plot) + 
  geom_rect(data = len0_plot, aes(xmin = preds$plower[1], xmax = preds$pupper[1], ymin = 0, ymax = Inf),
  fill = "grey80", alpha = 0.5) + geom_rect(data = len0_plot, aes(xmin = preds$lower[1],
  xmax = preds$upper[1], ymin = 0, ymax = Inf), fill = "grey60", alpha = 0.5) +
  geom_rect(aes(xmin = preds$len[1], xmax = preds$len[1], ymin = 0, ymax = Inf), col= "#F21A00") + ylim(0, 50) +
  geom_histogram(data = len0_plot, aes(x = STL, fill = species), binwidth = 2.5, col = "black") +
  facet_wrap(~ facet) + scale_fill_manual(values = c("#a1dab4", "#41b6c4")) + 
  guides(fill = guide_legend(title = NULL)) + theme(legend.position = c(0.21, 0.83),
  legend.text = element_text(face = "italic", size = rel(0.75))) + 
  xlab("TL (cm)") + ylab("Count") + lim_theme

p4 <- ggplot() + #geom_line(data = true_age, aes(x = age, y = dens_age), colour = "#F21A00") +
  geom_density(data = age2, aes(x = age, colour = Reader, fill = Reader), size = 1, alpha = 0.25) + 
  facet_wrap(~ facet) + scale_colour_manual(values = c("#a1dab4", "#225ea8")) +
  scale_fill_manual(values = c("#3B9AB2","#78B7C5")) +  ylab("Density") + xlab("Age (years") + 
  guides(fill = guide_legend(title = NULL), colour = guide_legend(title = NULL)) +
  theme(legend.position = c(0.81, 0.83)) + lim_theme

p3 <- ggplot(data = preds_both, aes(x = age, y= len,  colour = species, linetype = species,
  group = interaction(species, sex))) + geom_line() + scale_colour_manual(values = c("black", "black", "grey")) + 
  scale_linetype_manual(values = c("solid", "dotted", "solid")) + xlab("Age (years)") + ylab("TL (cm)") +
  guides(colour = guide_legend(title = NULL), linetype = guide_legend(title = NULL)) + theme(legend.position = 
  c(0.77, 0.20), legend.text = element_text(face = "italic", size = rel(0.75)))+ facet_wrap(~ facet) + lim_theme

p5 <- ggplot()+geom_point(data = nursery, aes(x = Month2, y= STL, fill = coh), shape =21) +
  scale_fill_manual(values = c("#ffffcc","#a1dab4", "#41b6c4", "#225ea8")) +
  geom_line(data = mon_pred, aes(x= Month2, y = Age, group = Cohort)) +
  ylab("TL (cm)") + xlab("") + facet_wrap(~ facet) + 
  scale_x_continuous(breaks = c(1:12), labels = c(month.abb[12], month.abb[-12])) +
  guides(fill = guide_legend(title = NULL)) + theme(legend.position = c(0.35, 0.91),
  legend.direction = "horizontal") + ylim(65, 140) + lim_theme

p6 <- ggplot(data = resids, aes(x = len_pred, y = resid)) + geom_point(pch = 21, fill = "#3B9AB2") +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  ylab("Residual (cm)") + xlab("Predicted TL (cm)") + facet_wrap(~facet) +
  lim_theme


grid.arrange(p, p1, p2, p6, p3, p5)

# Clean up environment
rm(df, nursery, qld_age_abt_f, qld_age_abt_m, qld_len_abt_f, qld_len_abt_m, 
   nt_age_abt_f, nt_age_abt_m, nt_len_abt_f, nt_len_abt_m, obj, parameters,
   opt, rep, preds, preds_abt, preds_both, true_age, len0_plot, len0, mon_pred,
   raw_points, raw_points_abt, max_f, max_m, CV, CVe, K, L0, Linf, list_data,
   age, age_dat, age2)
```


Fig 3.
\newpage
```{r fig4, fig.width = 8, fig.height = 3.5}
# Plots from length weight analysis

## Both sexes
p <- lw_both$plot + facet_wrap(~facet) + xlab("TL (cm)") + ylab("Weight (kg)") + xlim(50, 260) +
  ylim(0, 135) + lim_theme

# Comparison with C. tilstoni
data_all$facet = "(b) Species comparison - log scale"
p1 <- ggplot(data_all, aes(x = STL, y= Wgt, fill = Species)) + geom_point(shape = 21) + 
  scale_fill_manual(values = c("#a1dab4", "#41b6c4"), guide = guide_legend(title = NULL)) + 
  scale_y_log10(breaks = c(0.5, 1, 2, 5, 10, 20, 50, 100)) + scale_x_log10(breaks  = c(50, 75, 100, 150, 200, 250)) +
  xlab("TL (cm)") + ylab("Weight (kg)") + facet_wrap(~facet) + lim_theme + 
  theme(legend.position = c(0.20, 0.84), legend.text = element_text(face = "italic", size = rel(0.75)),
  legend.margin = margin(3,3,3,3, unit = "pt"))

grid.arrange(p, p1, nrow = 1)

# Clean up environment
rm(lw_m, lw_f, lw_both, lw_abt, lw_results, anova_lw, mod_lw, mod_lw2)
```
\
Fig 4.

\newpage

```{r fig5, fig.width = 8, fig.height = 7}
# Plots from maturity analysis
p <- lm_both$plot + facet_wrap(~ facet) + ylab ("Proportion mature") + xlab("TL (cm)") +
  lim_theme

p1 <- am_both$plot + facet_wrap(~ facet) + ylab ("Proportion mature") + xlab("Age (years)") +
  lim_theme

lm_comparison <- select(lm_results, Species, Sex, L50, L50_lower, L50_upper, facet) %>% slice(3:9)

p2 <- ggplot(lm_comparison, aes(x = Species, y = as.numeric(L50), ymin = L50_lower, ymax = L50_upper)) + 
  geom_errorbar(aes(fill = Species, shape = Sex), width = 0.1, position = position_dodge(width = 0.5)) + 
  geom_point(aes(fill = Species, shape = Sex), position = position_dodge(width = 0.5), size = 2) + 
  scale_fill_manual(values = c("#ffffcc", "#a1dab4","#41b6c4"), guide = "none") + 
  scale_shape_manual(values =c(21,22,23,24), guide = guide_legend(title = NULL))+
  xlab("") + ylab(bquote(italic(L)[50]~"(mm)")) + theme(legend.position = c(0.22, 0.75), 
  legend.text = element_text(size = rel(0.75)), axis.text.x = element_text(face = "italic")) + 
  facet_wrap(~ facet) + lim_theme

am_comparison <- select(am_results, Species, Sex, A50 = L50, A50_lower = L50_lower, A50_upper = L50_upper, facet) %>% 
  slice(3:9)

p3 <- ggplot(am_comparison, aes(x = Species, y = as.numeric(A50), ymin = A50_lower, 
   ymax = A50_upper)) + 
  geom_errorbar(aes(fill = Species, shape = Sex), width = 0.1, position = position_dodge(width = 0.5)) + 
  geom_point(aes(fill = Species, shape = Sex), position = position_dodge(width = 0.5), size = 2) + 
  scale_fill_manual(values = c("#ffffcc", "#a1dab4","#41b6c4"), guide = "none") + 
  scale_shape_manual(values =c(21,22,23,24), guide = "none") +
  xlab("") + ylab(bquote(italic(A)[50]~"(years)")) + theme(legend.text = element_text(size = rel(0.75)), 
  axis.text.x = element_text(face = "italic")) + facet_wrap(~ facet) + lim_theme

gridExtra::grid.arrange(p, p1, p2, p3, nrow = 2)

# Clean up environment
rm(am_f, am_m, am_both, am_abt_f, am_abt_m, am_both, amatern_abt, lm_f, lm_m, lm_both, lm_abt_f, lm_abt_m,
   lmatern_abt, mod_am, mod_am2, mod_lm, mod_lm2, L50, L95)
```
\
Fig 5.

\newpage

```{r fig6, fig.width = 10, fig.height=8}
## Demographic analysis plots

## Plot A. Density of r intrinsic values using ridgeplot
r_plot <- mutate(monte_carlo, plot_title = "(a) Intrinsic rate of population increase ")

p <- ggplot(r_plot, aes(x = r_int, y = species, fill = species)) +
  geom_density_ridges() + scale_fill_manual(values = c("#ffffcc", "#a1dab4","#41b6c4")) +
  theme(legend.position = "none", axis.text.y = element_text(face = "italic")) + lim_theme +
  xlab(bquote(italic(r) ~ "(year"^"-1" ~ ")")) + ylab("") + facet_wrap(~plot_title)

## Plot B. R intrinsic versus mortality

# Relationship between r intrinsic and mortality
m_r_int <- mutate(m_r_int, plot_title = "(b) Intrinsic rate of population increase vs female mortality") %>%
  ungroup() %>%
  mutate(species = factor(species, levels = c("C. tilstoni (NT)", "C. tilstoni (QLD)", "C. limbatus")))

# Mean and CI of r intrinsic and M from Monte Carlo simulations
confints <- group_by(monte_carlo, species) %>%
  summarise(
    r_int_mean = mean(r_int), upper_r_int = quantile(r_int, 0.975), lower_r_int = quantile(r_int, 0.025),
    M_f_mean = mean(M_f), upper_M = quantile(M_f, 0.975), lower_M = quantile(M_f, 0.025)
  )

p3 <- ggplot() + facet_wrap(~plot_title) +
  geom_errorbar(data = confints, aes(x = M_f_mean, ymin = lower_r_int, ymax = upper_r_int)) +
  geom_errorbarh(data = confints, aes(x = M_f_mean, y = r_int_mean, xmin = lower_M, xmax = upper_M)) +
  geom_point(data = confints, aes(x = M_f_mean, y = r_int_mean, fill = species), pch = 21) +
  geom_line(data = m_r_int, aes(x = M_f, y = r_int, group = Pmax, colour = species)) +
  annotate("segment", x = 0.07, xend = 0.1, y = 0.025, yend = 0.05, size = 0.5, arrow = arrow(length = unit(0.020, "npc"))) +
  annotate("segment", x = 0.12, xend = 0.15, y = 0.025, yend = 0.05, size = 0.5, arrow = arrow(length = unit(0.020, "npc"))) +
  annotate("text", x = 0.04, y = 0.02, label = "Biennial") +
  annotate("text", x = 0.10, y = 0.02, label = "Triennial") +
  scale_colour_manual(values = c("#ffffcc", "#a1dab4","#41b6c4")) +
  scale_fill_manual(values = c("#ffffcc", "#a1dab4","#41b6c4")) +
  guides(fill = "none") +
  ylab(bquote(italic(r) ~ "(year"^"-1" ~ ")")) +
  xlab(bquote(italic(M[f]) ~ "(year"^"-1" ~ ")")) +
  theme(
    legend.position = c(0.80, 0.80), legend.title = element_blank(),
    legend.text = element_text(face = "italic", size = rel(0.75))
  ) +
  lim_theme

## Plots C and D. Stable age distributions

sad_plot <- group_by(monte_carlo, species) %>% 
  select(species, sad_f, sad_integral_f, sad_m, sad_integral_m) %>%
  mutate(id = row_number()) %>% unnest(sad_m, sad_f) %>% select(-age1) %>%
  rename(male.weight = weight, female.weight = weight1, 
         male.len = length, female.len = length1, 
         male.mat = maturity, female.mat = maturity1,
         male.spawn = maternity, female.spawn = maternity1) %>% 
  mutate(male.weight = male.weight / sad_integral_m, 
         female.weight = female.weight / sad_integral_f) %>% 
  select(-sad_integral_m, -sad_integral_f, - male.spawn) %>% 
  gather(key = "key", value = "proportion", -id, -species, -age) %>%
  separate(key, into = c("sex", "variable")) %>% ungroup %>% 
  spread(variable, proportion) %>%
  arrange(species, sex, age) %>%
  group_by(species, sex, age) %>% 
  summarise(length = mean(len), prop = mean(weight), 
            prop.mature = mean(mat), prop.spawn = mean(spawn)) %>%
  mutate(prop.mature = prop * prop.mature) %>%
  mutate(prop.spawn = prop * prop.spawn) %>%
  unite(species_sex, c("species", "sex"), sep = " - ", remove = FALSE) %>% ungroup %>% 
  mutate(species_sex = fct_relevel(species_sex, "C. tilstoni (NT) - male", "C. tilstoni (NT) - female", 
                                   "C. tilstoni (QLD) - male", "C. tilstoni (QLD) - female",
                                   "C. limbatus - male", "C. limbatus - female"))  %>%
  gather(key = biomass_type, value = biomass, - species_sex, -species, -sex, - age, -length) %>%
  mutate(species = ifelse(species %in% "C. limbatus", "C. limbatus", "C. tilstoni")) %>%
  mutate(region = ifelse(species_sex %in% c("C. tilstoni (NT) - female", "C. tilstoni (NT) - male"), "(NT)", " ")) %>%
  mutate(region = ifelse(species_sex %in% c("C. tilstoni (QLD) - female", "C. tilstoni (QLD) - male"), "(QLD)", region)) %>%
  mutate(label = factor(paste("paste(italic(\"", species, "\"), \" ", region, " - ", sex, "\")", sep = ""))) %>%
  mutate(plot_title = "(c) Stable age distribution vs Age") %>%
  mutate(plot_title2 = "(d) Stable age distribution vs Length") %>% 
  filter(!is.na(biomass))

labs <- levels(sad_plot$label) 
labs <- labs[c(1,2,5,6,3,4)]
labs <- parse(text = labs)


p1 <- ggplot() +
  geom_ridgeline(data = sad_plot, aes(x = age, y = species_sex, 
                                  height = biomass, alpha = biomass_type,
                                  fill = species_sex), scale = 7.5) +
  scale_y_discrete("", labels = rev(labs)) +
  scale_fill_manual(values = c("#ffffcc", "#ffffcc", "#a1dab4", "#a1dab4", "#41b6c4", "#41b6c4")) + xlim(0, 30) + 
  scale_alpha_manual(values = c(0.4, 0.7, 1)) + 
  theme(legend.position = "none", 
        axis.text.y = element_text(size = rel(0.85))) + 
  xlab("Age (years)") + 
  facet_wrap(~ plot_title) + lim_theme


p2 <- ggplot() +
  geom_ridgeline(data = sad_plot, aes(x = length, y = species_sex, 
                                  height = biomass, alpha = biomass_type,
                                  fill = species_sex), scale = 7.5) +
  scale_y_discrete("", labels = NULL) +
  scale_fill_manual(values = c("#ffffcc", "#ffffcc", "#a1dab4", "#a1dab4", "#41b6c4", "#41b6c4")) +
  scale_alpha_manual(values = c(0.4, 0.6, 1)) + 
  annotate("segment", x = 200, xend = 135, y = 3, yend = 2.65, size = 0.5, arrow = arrow(length = unit(0.020, "npc"))) +
  annotate("segment", x = 215, xend = 150, y = 2.65, yend = 2.3, size = 0.5, arrow = arrow(length = unit(0.020, "npc"))) +
  annotate("text", x = 215, y = 3, label = "Mature") +
  annotate("text", x = 235, y = 2.65, label = "Maternal") +
  theme(legend.position = "none") + 
  ylab("") + xlab("TL (cm)") + 
  facet_wrap(~ plot_title2) + lim_theme

gA <- ggplotGrob(p)
gB <- ggplotGrob(p1)
gC <- ggplotGrob(p2)
gD <- ggplotGrob(p3)

gAC <- do.call(rbind, c(list(gA, gB), size = "first"))
gBD <- do.call(rbind, c(list(gD, gC), size = "first"))

grid::grid.newpage()
grid.arrange(gAC, gBD, ncol = 2, widths = c(0.55, 0.45))
```

\
Fig 6.

